A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-18 tex/body.tex
shorten

Datatypes and codatatypes are an integral part of most modern proof assistants,
including Agda, Coq, Isabelle, Matita, and PVS. In recent years, datatypes
have emerged in a few automatic theorem provers as well. The SMT-LIB
\cite{barrett-et-al-2010} format, implemented by most SMT %(satisfiability
%modulo theories)
solvers, has been extended with a syntax for datatypes.

@@

%\paragraph{Characterization.}
One way to define datatypes semantically is as the initial model of the
selector--constructor equations \cite{barrett-et-al-2010}.
\begin{rep}
A drawback of this approach is that it does
not naturally account for selectors applied to wrong constructors. Barrett et
al.\ address this by parameterizing the construction by default values, but
this gives rise to spurious equalities between unrelated terms---e.g.,
$\const{s}_1^1(\const{C}_2) \teq \const{s}_1^1(\const{C}_3)$. This flaw
could be corrected, but the added complexity seems to suggest that selectors
are better characterized axiomatically.

>>>>

Datatypes and codatatypes are an integral part of most modern proof assistants,
including Agda, Coq, Isabelle, Matita, and PVS. In recent years, datatypes
have emerged in a few automatic theorem provers as well. The SMT-LIB
%\cite{barrett-et-al-2010}
format, implemented by most SMT
%(satisfiability modulo theories)
solvers, has been extended with a syntax for datatypes.

@@

%\paragraph{Characterization.}
One way to define datatypes semantically is as the initial model of the
selector--constructor equations \cite{barrett-et-al-2007}.
\begin{rep}
A drawback of this approach is that it does
not naturally account for selectors applied to wrong constructors. Barrett et
al.\ address this by parameterizing the construction by default values, but
this gives rise to spurious equalities between unrelated terms---e.g.,
$\const{s}_1^1(\const{C}_2) \teq \const{s}_1^1(\const{C}_3)$. This flaw
could be corrected, but the added complexity seems to suggest that selectors
are better characterized axiomatically.
